---
title: "BUS 696 ASSIGNMENT"
author: "R"
date: "10/3/2021"
output: html_document
---
## QN 1a
```{r}
library(readr)
X433555401_IMDB_movies_3746998591142155 <- read_csv("C:/Users/Admin/Downloads/433555401_IMDB_movies_3746998591142155.csv")
imdb<-X433555401_IMDB_movies_3746998591142155
head(imdb)
```

```{r}
library(dplyr)
imdb<-imdb %>% 
  mutate(grossM=gross/1000000)


imdb<-imdb %>% 
  mutate(budgetM=budget/1000000)

imdb<-imdb %>% 
  mutate(log_gross=log(gross))
imdb<-imdb %>% 
  mutate(log_budget=log(budget))
names(imdb)
```

## QN1b

```{r}
library(forcats)
imdb$rating_factor <- fct_explicit_na(imdb$content_rating)
movies_clean<-imdb[,c(29,30,31,32)]
movies_clean$rating_factor<-imdb$rating_factor
````

## QN 1c
```{r}
movies_clean$rating_simple<-fct_lump_n(movies_clean$rating_factor,n=4)
```

## QN 1d

```{r}
x<-table(imdb$content_rating,movies_clean$rating_simple)
x 
```

## QN 1e

```{r}
library(rsample)
set.seed(1234)         
movie_split<-initial_split(movies_clean)
movies_train<-training(movie_split)
movie_test<-testing(movie_split)
````

1f

This is important forevaluation of the data mining models, When a data set is divided into a training set and a testing set, the majority of the data is used for training and a smaller amount is utilized for testing. Analysis procedure takes a random sample of the data to guarantee that the training and testing sets are comparable. You can reduce the effects of  i.e KNN data discrepancies and gain a better understanding of the model's properties by using similar data for training and testing.

## QUESTION 2

```{r}
 mod1<-lm(grossM~imdb_score,data = imdb)
summary(mod1)
```

## Qn 2b

An positive increase of one unit of the gross results to a a positive increase of 13.978 units of IMDB score

## Qn 2c
 The p_value measures if the model carries any statistical significance
 
##Qn 2d

p-value- 2e-16 *** The relationship between imdb and gross can be assessed because its statistically significant

```{r}
mod2<-lm(log_gross~imdb_score,log_budget,title_year,data =imdb)

```

## Qn 2f
```{r}
summary(mod2)
```

## Question 2h

The column rating_simpeG is a character variable sand cannot be estimated 
on model.extract

## Question 2i
An positive increase of one unit of the log_budget_M results to a a positive increase of 0.93179 units of IMDB score

## Question 2j

The coefficient suggest there has been a positive return on the investments

## Question3

```{r}
preds_train<-predict(mod2,newdata =imdb )
head(preds_train)

preds_test<-predict(mod1,newdata = imdb)
head(preds_test)
```

## 3b and 3c

```{r}
get_rmse<-function(true_values,predictions){
  sqrt(mean((exp(true_values)-exp(predictions))^2))
}

get_mae<-function(true_values,predictions){
  mean(abs(true_values-predictions))

}
head(movies_train)
head(preds_train)

y<-get_rmse(preds_test,preds_train)
y

w<-get_mae(preds_test,preds_train)
w
```

## 3d

```{r}
results<-data.frame('preds'=c(exp(preds_test),exp(preds_train)),
                    'true'=c(movie_test$grossM,movies_train$grossM),
                    'type'=c(rep("Test",nrow(movie_test)),rep("Train",nrow(movies_train))))%>%mutate(preds=preds/1e6,true=true/1e6)
head(results)
```

## 3e

```{r}
library(ggplot2)
plot<-ggplot(results,aes(y=preds,x=true))+geom_point(alpha=1/20)+
  xlim(0,300)+ylim(0,300)+geom_abline(aes(intercept = 0,slope= 1),linetype="dashed")+
  facet_wrap(~type)+theme_minimal()+labs(x="True Movie Gross($M USD",
                                         y="Predicted Movie Gross($M USD")
plot
```

